Recurrence spike spectra

### 2022-06-10 Manuscript/inter_spike_manuscript.tex
CENOGRID computed spectrograms and ISS spectrogram (.mat)-files ignored

\begin{figure}[h]
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_dirac_comb}
 \caption{The transformation of a Dirac comb (series of Dirac delta functions) with a single inter-spike period $T_{\text{is}}=100$ ($\widehat{=}f=0.01$) 
 into the frequency domain. 
 \textbf{A} Dirac Comb (DC) with equal amplitudes and
 \textbf{B} its FFT-based powerspectrum.
 \textbf{C} Proposed inter spike spectrum of the signal in \textbf{A} showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
 \textbf{D} DC with randomly chosen amplitudes and same $T_{\text{is}}$ as in \textbf{A}, and
 \textbf{E} its FFT-based powerspectrum. 
 \textbf{F} Proposed inter spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
 Inter spike spectra were obtained with a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and its re-composed signals. 
}
\label{fig_tau_rr_dirac_comb}
\end{figure}

@@

\noindent Eventually, an under-determined linear system
\begin{equation}
\bf{X}^T\bf{\beta}=\bf{s}
\label{eq_linear_system}
\end{equation}  
has to be solved for $\bf{\beta}$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
particularly interested in those solutions, which promote sparsity in $\bf{\beta}$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). Therefore, we here choose the \textit{least absolute shrinkage and selection operator} 
(LASSO regression) \cite{Tibshirani1996} to obtain a solution $\hat{\bf{\beta}}$. Finally, we group loadings which correspond to basis functions having the same period 
$T_\text{is}$ into $\hat{\bf{\beta}}_f$ and obtain the 
\textit{inter spike spectrum} by simply plotting $\hat{\bf{\beta}}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$ 
(Fig.~\ref{fig_tau_rr_dirac_comb}C, F).

@@

\begin{figure}
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler}
 \caption{Inter spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
 Trajectory of the system in a \textbf{A} period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
 \textbf{C} in a chaotic regime (parameter $a=0.428$). 
 \textbf{D, E, F} The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
 recurrence rate for D \& E and 5\% for F. 
  \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a regularization threshold corresponding to 
  $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
 }
\label{fig_tau_rr_example_roessler}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_tau_rr_logistic}
 \caption{\textbf{A} Lyapunov exponent of the Logistic map as a function of the control parameter $r$. 
 \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in \textbf{A} 
 (white noise surrogates). 
 \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}. For obtaining the inter spike spectra we used 
 a regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals.  
}
\label{fig_tau_rr_logistic}
\end{figure}

>>>>

\begin{figure}[h]
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_dirac_comb}
 \caption{The transformation of a Dirac comb (series of Dirac delta functions) with a single inter-spike period $T_{\text{is}}=100$ ($\widehat{=}f=0.01$) 
 into the frequency domain. 
 \textbf{A} Dirac Comb (DC) with equal amplitudes and
 \textbf{B} its FFT-based powerspectrum.
 \textbf{C} Proposed inter spike spectrum of the signal in \textbf{A} showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
 \textbf{D} DC with randomly chosen amplitudes and same $T_{\text{is}}$ as in \textbf{A}, and
 \textbf{E} its FFT-based powerspectrum. 
 \textbf{F} Proposed inter spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
 Inter spike spectra were obtained with a LASSO regression and a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and 
 its re-composed signals (c.f. Section~\ref{sec_tau_rr_method}). 
}
\label{fig_tau_rr_dirac_comb}
\end{figure}

@@

\noindent Eventually, an under-determined linear system
\begin{equation}
\bf{X}^T\bf{\beta}=\bf{s}
\label{eq_linear_system}
\end{equation}  
has to be solved for $\bf{\beta}$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
particularly interested in those solutions, which promote sparsity in $\bf{\beta}$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\bf{\beta}}$. Finally, we group loadings 
which correspond to basis functions having the same period 
$T_\text{is}$ into $\hat{\bf{\beta}}_f$ and obtain the 
\textit{inter spike spectrum} by simply plotting $\hat{\bf{\beta}}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$ 
(Fig.~\ref{fig_tau_rr_dirac_comb}C, F).

@@

\begin{figure}
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler}
 \caption{Inter spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
 Trajectory of the system in a \textbf{A} period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
 \textbf{C} in a chaotic regime (parameter $a=0.428$). 
 \textbf{D, E, F} The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
 recurrence rate for D \& E and 5\% for F. 
  \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a LASSO regression and a regularization threshold 
  corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
 }
\label{fig_tau_rr_example_roessler}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_tau_rr_logistic}
 \caption{\textbf{A} Lyapunov exponent of the Logistic map as a function of the control parameter $r$. 
 \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in \textbf{A} 
 (white noise surrogates). 
 \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}. For obtaining the inter spike spectra we used 
 a LASSO regression and a regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals.  
}
\label{fig_tau_rr_logistic}
\end{figure}
